Portal Forecast

### 2017-09-20 index.Rmd

for (species in as.vector(most_abund_sp$species)) {
  species_forecast = forecast_viz(obs_data = obs_data_newmoon,
               obs_date_col_name = "newmoonnumber",
               obs_val_col_name = species,
               for_data = for_data,
               for_date_col_name = "newmoonnumber",
               for_val_col_name = "estimate",
               for_model_name = "ensemble",
               for_lowerpi_col_name = "LowerPI",
               for_upperpi_col_name = "UpperPI",
               start_newmoon = 300)
  plot(species_forecast)
}
```

>>>>

for (species in as.vector(most_abund_sp$species)) {
  species_forecast = forecast_viz(obs_data = obs_data_newmoon,
               obs_date_col_name = "censusdate",
               obs_val_col_name = species,
               for_data = for_data,
               for_date_col_name = "forecastdate",
               for_val_col_name = "estimate",
               for_model_name = "ensemble",
               for_lowerpi_col_name = "LowerPI",
               for_upperpi_col_name = "UpperPI",
               start_newmoon = 300)
  plot(species_forecast)
}
```
